Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-10-02 manuscript/paper-tycho.tex
Update Tycho fit data/spectra, paper results/disc
Finish pipelining all Tycho data, updated tables/plots
Incorporate all manuscript comments, tidy text up to results, flesh out
discussion.

%\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
% \documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
% \documentclass[iop, apj, numberedappendix]{emulateapj}

@@

\usepackage{amsmath}  % amsthm, amssymb
% \usepackage{CJK}  % aas.org/authors/author-names-non-roman-alphabets
\usepackage{booktabs}
%\usepackage[labelfont=bf, labelsep=period]{caption}  % Custom float captions
%\usepackage{pdflscape}  % rotate pages (Texlive)
\usepackage{hyperref}

\newcommand*{\mt}{\mathrm}
\newcommand*{\unit}[1]{\;\mt{#1}}  % http://vemod.net/typesetting-units-in-latex
\newcommand*{\abt}{\mathord{\sim}} % http://tex.stackexchange.com/q/55701
\newcommand*{\ptl}{\partial}
\newcommand*{\del}{\nabla}

@@

\begin{document}

@@

%\begin{CJK*}{UTF8}{gbsn}
\author{
Aaron Tran\altaffilmark{1,4},
Brian J. Williams\altaffilmark{1,5},
Robert Petre\altaffilmark{1},
Sean M. Ressler\altaffilmark{2},
Stephen P. Reynolds\altaffilmark{3}
}
%\end{CJK*}

@@

%\altaffiltext{1}{NASA Goddard Space Flight Center, Greenbelt, MD 20771, USA}
%\altaffiltext{2}{Dept. Physics, University of California,
%    Berkeley, CA 94720, USA}
%\altaffiltext{3}{Dept. Physics, North Carolina State University,
%    Raleigh, NC 27695, USA}
\altaffiltext{4}{CRESST, University of Maryland, College Park, MD 20742}
\altaffiltext{5}{NASA Postdoctoral Program Fellow}

@@

% Intro -- shocks, DSA, thin rims, filament observations; other fields/work
Forward shock accelerated electrons in young supernova remnants (SNRs) emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream, producing a shell-like morphology with bright X-ray and radio
rims/filaments due to line-of-sight projection \citep{koyama1995}.  Although
synchrotron emission due to accelerated electrons does not imply acceleration
of an unseen hadronic component, the prevailing theory of diffusive shock
acceleration (DSA) should operate on both protons and electrons.  Observations
of these synchrotron rims, with other lines of direct and indirect evidence,
have built a case for hadron and lepton acceleration up to $\unit{PeV}$
energies in young supernova remnants \citep{uchiyama2007, aharonian2004,
acero2010, ackermann2013} \note[Aaron]{up to PeV energies for both populations?
Do protons reach higher energies with lower synchrotron losses?}. Efficient
hadron acceleration, if able to convert $\abt10\%$ of a supernova's $10^{51}
\unit{erg}$, is a prime candidate source for galactic cosmic rays up to the CR
spectrum ``knee'' \citep{vink2012}.

Spectral and spatial measurements of synchrotron rims can help constrain
physical parameters of the shock acceleration process.  Many previous workers
have inferred strong magnetic field amplification at SNR shocks, as electrons
must radiate energy rapidly to account for the thinness of observed rims.
\note[Aaron]{flesh out} Plasma physics details -- Bell's cosmic ray current
instability \citep{bell2001} ties magnetic field amplification w/ maximum CR
energy (push towards and just above the PeV limit).  How to get large
compression ratios (why is 10 an upper bound suggested by Parizot), magnetic
fields -- how far can amplification go?
The processes observed in SNR shocks are broadly relevant to many collisionless
astrophysical shocks, such as Earth's bow shock, stellar wind-blown bubbles,
starburst galaxies \citep{heckman1990}, jets of active galactic nuclei, galaxy
clusters \citep{van-weeren2010}, and even cosmological shocks
\citep{miniati2000, ryu2008}.  Reviews of diffusive shock acceleration have
ably highlighted the ubiquity of shock acceleration in astrophysical settings
\note[Aaron]{too trite?} \citep[e.g.,][]{blandford1987, malkov2001}.

% What makes these shocks?
The widths of these X-ray rims are thought to be controlled by a combination of
synchrotron losses, particle transport, and magnetic fields immediately
downstream of the shock.  Synchrotron losses depend on the initial electron
energy distribution and the gradual decrease of electron energies downstream of
the shock.  High energy electrons near the shock efficiently radiate harder
synchrotron X-ray photons, but decline in energy as they are transported away
from the shock; this may be seen in spectral softening downstream of the shock
\citep[e.g.,][]{cassam-chenai2007}.  The transport process is driven by bulk
plasma advection downstream of the shock and particle diffusion with respect to
bulk advection.  In general, diffusion allows higher energy electrons to
diffuse further upstream or downstream than would be expected from pure
advection.  Finally, the magnetic field strength may be quickly damped behind
the shock, so that electrons may not radiate as efficiently and thin rims would
reflect the spatial structure of the field, rather than efficient particle
acceleration (and losses) and/or efficient synchrotron cooling
\citep{pohl2005}.

% Energy dependence.
Moreover, these controlling mechanisms predict different scalings for rim width
as a function of energy.  Synchrotron loss-limited rims should scale as $w
\propto \nu^{-1/2}$.  Diffusion smears out rims at all energies with stronger
effect at higher energies, yielding a slower drop-off in rim widths when
diffusion dominates.  Magnetic damping, if at a length scale comparable to
filament widths, predicts comparatively energy-independent rim widths --
intuitively, if the magnetic field turns off, synchrotron radiation turns off
regardless of electron energy.  \note[Aaron]{this would benefit from
numbers/quantification, I think this statement is stronger if the magnetic
field is stronger -- compare Figure 1 of \citet{pohl2005}} \citet{ressler2014}
give a much fuller exposition of the relative effects of advection, diffusion,
and magnetic field damping on filament rim widths.

% Which one is right?
Previous work has used the typical scale width of the filaments to derive
magnetic field estimates, among other physical parameters.  Observed
synchrotron spectrum roll-offs at X-ray energies require corresponding cut-offs
in the electron spectrum \citep{reynolds1998}; such a cut-off is naturally
predicted by DSA balanced against synchrotron losses, and requires that
diffusion and advection are both important near the electron cut-off energy
\note[Aaron]{imprecise statement...} Whether accounting for advection and
diffusion independently, or jointly in more sophisticated transport models, It
became clear that magnetic field amplification was necessary to explain the
observed filaments \citet{bamba2003, vink2003, parizot2006}.  \note[Aaron]{this
is said 3 paragraphs above already}

% Magnetic damping...
Magnetic damping immediately behind the shock offers a tantalizing alternative
explanation for filament rims that requires less extreme magnetic field
amplification, and damping has not been fully tested \citep{pohl2005,
marcowith2010}.  \citet{cassam-chenai2007} examined radio and X-ray synchrotron
rim profiles, but found that neither damping nor synchrotron losses matched
radio profiles particularly well.  \citet{araya2010} measured rims at multiple
energy bands in Cas A, but suggested that the rims only narrow more weakly than
expected and did not consider magnetic damping.  \citet{rettig2012} gave model
predictions for several historical SNRs and proposed discriminating based on
filament spectra -- the expectation is that damped spectra are softer,
loss-limited harder.  \citet{ressler2014}, using deep observations of SN 1006
from a recent \Chandra Large Project, fully developed the idea of
differentiating damping and loss-limited scenarios by using rim width energy
dependence and found rim narrowing in the remnant of SN 1006, strongly favoring
a loss-limited model.

% Why Tycho's SNR
To further test these models, we follow \citet{ressler2014} by measuring rim
widths at multiple energies in the remnant of Tycho's 1572 supernova
(hereafter, Tycho).  Tycho, being a nearby galactic SNR, is close enough that
its rims are well-resolved by \textit{Chandra}'s spatial resolution; the work
is further made possible by a deep $750 \unit{ks}$ exposure of the entire
remnant, yielding excellent count rates and allowing us to sample the rims
quite finely.  Tycho has an extensive and unusually contiguous shell of
synchrotron rims around its periphery, consistent with expansion into a low
density ISM.  \citet{williams2013} favor mean pre-shock ISM density $\abt
0.1$--$0.2 \unit{cm^{-3}}$, consistent with Tycho's X-ray expansion rate
\citep{katsuda2010}.  Although Tycho is expanding into an ISM gradient
\citep{williams2013} and interacting with a molecular cloud on its eastern limb
\citep{reynoso1999}, Tycho's spherical morphology suggests that we might expect
more consistent shock acceleration around its periphery than in other
historical remnants, whether of Type Ia or CC SNe.

Evidence for acceleration: basically, see \citet{morlino2012} for a nice review
of evidence in Tycho.  No need to cite everything here.

spectral softening \citep{cassam-chenai2007}, CD-FS gap \citep{warren2005},
multi-wavelength observations \citep{acero2010, acciari2011, morlino2012} for
SN 1006 and Tycho; Tycho's tiger stripes \citep{eriksen2011}. These further
support the notion that Tycho is actively accelerating hadrons and leptons.
Various questions to consider (or answer).  Why the diversity of filament
structure? How does diffusion really work?  How much energy is going into
cosmic rays / how efficient is the acceleration process?  All sorts of
things... (one interesting paper: \citet{caprioli2013}).
\note[Aaron]{this para may not be necessary}

% Paper roadmap
Our measurements and modeling closely followed and extended the procedure of
\citet{ressler2014} (hereafter, \citetalias{ressler2014}).  We first briefly
review relevant transport models which fully account for electron advection and
diffusion with continuous synchrotron losses, as considered by, e.g.,
\citet[and references therein]{berezhko2004} and \citet{rettig2012}.
We selected and measured rim widths at several locations around Tycho's forward
shock, verifying that selected rims are free of thermal line emission.  Using
our model for particle transport (with DSA included, to first order, in a
simple exponentially cut-off injected electron spectrum), we obtain estimates
on magnetic field strength and diffusion coefficient as a function. \emph{We
discuss the implications of our model fit results for particle transport in
Tycho, despite a significant degeneracy between diffusion and synchrotron
losses when diffusion is non-negligible.}
\note[Aaron]{(tentative?)}
\note[Aaron]{(non sub-Bohm, or anything above Bohm basically)}

@@

% TODO Chunk of text I don't know what to do with...
We consider two models for particle transport to our measurements of Tycho's
filament widths.  To best quantify width-energy dependence, we measure rim full
widths at half maximum (FWHMs) (Section~\ref{sec:fwhms}) and fit the
measurements to these models' predictions of rim FWHMs at multiple photon
energies.  \citetalias{ressler2014} give a fuller review of previous approaches
to characterizing filament widths, as well as a more thorough exposition of
model parameters and physical implications.

@@

% TODO Choose names for these models and refer to them consistently, throughout
% TODO define ALL symbols, synchrotron constants, etc (somewhere state that CGS
%      notation is being used)
% TODO double check equations, exposition against Rettig/Pohl and others
% TODO review variable definitions when closer to final draft
\note[Aaron]{\citet{blandford1987} and other papers take a much more thorough
tack in deriving the relevant transport equations, drawing specifically from
plasma physics / DSA assumptions -- I suppose much material is not relevant or
condensed into our diffusion coefficient $D$ (w/ stated Bohm diffusion).
Is na\"ively citing generalized ``transport'' is sufficient here?
E.g., there is often a term of form $E/3 (\del\cdot\vec{v}) (\ptl f/\ptl E)$,
neglected for steady downstream velocity (i.e., $\del\cdot\vec{v}=0$), which
would not arise out of our equations as stated.
See, e.g., equation (9) of \citet{skilling1975}.}
% Transport fundamentals
The energy and space distribution of electrons at a supernova remnant
controls the synchrotron rims we see in X-ray and radio.  We model electron
transport from initial injection at the remnant's forward shock as following
an advection-diffusion equation given by:
\begin{equation}
  \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
  = C + \del \cdot \left( D \del f \right)
\end{equation}
where $f = f(E,x)$ is electron distribution as a function of electron energy
$E$ and downstream distance $x$ (where the forward shock is at $x=0$ and
$x>0$ towards the remnant's interior); $C$ is an arbitrary source/sink term,
$D$ is the diffusion coefficient, and $\vec{v}$ is a velocity field.
By considering 1-D steady-state plane transport at a constant downstream
velocity $v_d$ and a space-independent diffusion coefficient, we obtain:
\begin{equation}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
\end{equation}
For simplicity, the source/sink term $C$ and diffusion coefficient $D$
encapsulate all assumptions about the DSA-generated electron spectrum, shock
and magnetic field structure, and time/space evolution of the particle
distribution.  We also consider only particle transport downstream of the
shock ($x \geq 0$).  More sophisticated treatments may explicitly treat
magnetic fields across the shock, plasma streaming instabilities and particle
losses, anisotropic diffusion, the DSA process and efficiency, and other
details in great depth \citep[e.g.,][and references therein]{reville2013,
bykov2014, ferrand2014}.

% Simple model
A first approximation is to let electrons have constant energy that is dumped
catastrophically after a synchrotron timescale $\tsynch = 1/(b B^2 E)$, where
$b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
vary as $B=B(x)$).  The sink term is $C = -f / \tsynch$, yielding:
\begin{equation} \label{eq:simp-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0 .
\end{equation}
No assumptions on the injected electron source term are necessary
\note[Aaron]{I don't have a citation, but it seems simple enough?}.
\citet{parizot2006} employed this model to derive estimates of magnetic fields,
diffusion coefficients, and electron spectrum cut-offs for several historical
SNRs.  Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f
\propto \exp(-x/a)$ where $a$ is a characteristic scale length.  The thin rim
FWHM predicted by equation~\eqref{eq:simp-mod} is:
\begin{equation} \label{eq:simp-fwhm}
    w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
\end{equation}
with $\beta$ a projection factor relating $w$ to $a$ as $w = \beta a$
\citep{berezhko2004, parizot2006}.  We take $\beta = 4.6$ assuming a spatially
exponential $f(E,x)$ and projection from a spherical shell, as derived by
\citet{ballet2006}.

% Full model
A more accurate model accounts for continuous synchrotron losses as electrons
are injected from an exponentially cut-off power-law electron distribution
(normalization $K_0$, cut-off energy $\Ecut$) and transported downstream:
\begin{align} \label{eq:full-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =\;
    &K_0 E^{-s} e^{-E/\Ecut} \delta(x) \nonumber \\
    &+ \frac{\ptl}{\ptl E} \left(bB^2E^2f\right) ;
\end{align}
see \citet{berezhko2004, cassam-chenai2007, morlino2010, rettig2012}; and
references therein.  The cut-off energy is determined by the form of the
diffusion coefficient $D$, which we discuss in Section~\ref{sec:diffcoeff}.
(but, cf. \citet{zirakashvili2007} on the exponential cut-off assumption) To
determine rim profiles and widths, we first numerically solve for electron
distribution $f(E,x)$ using Green's function solutions by \citet{lerche1980}
and \citet{rettig2012}; these solutions are given by \citetalias{ressler2014}
using notation similar to that used herein \note[Aaron]{wording}.  The electron
distribution may then be integrated to obtain synchrotron emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron emissivity
with $K_{5/3}(z)$ a modified Bessel function of the second kind
\citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
spherical remnant yields intensity as a function of radial coordinate $r$:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.  A model FWHM may then be calculated
from the resulting intensity profile.

In what follows we consider both transport models, but primarily present
results from the more advanced model (equation~\eqref{eq:full-mod}) as we find
the qualitative behavior of both models is comparable.

@@

\note[Aaron]{can condense this, merge first 2 paragraphs here?}
The modus operandi of much previous work has been to assume Bohm diffusion or
diffusion-energy scaling ($D \propto E$).  Bohm diffusion assumes that the
particle mean free path $\lambda$ is equal to the gyroradius $r_g = E/(eB)$,
yielding diffusion coefficient $D_{\mt{B}} = \lambda c / 3 = c E / (3 e B)$.
We may generalize by adding a prefactor $\eta$ such that $\lambda = \eta r_g$:
\begin{equation} \label{eq:bohm}
    D = \frac{\lambda c}{3} = \frac{\eta c E}{3 e B} .
\end{equation}
Here, and throughout, we use CGS (Gaussian) units; $c$ is the speed of light,
$E$ is particle energy, $e$ is elementary charge, and $B$ is magnetic field.
Bohm diffusion at $\eta = 1$ is commonly considered a lower
limit on the diffusion coefficient at all energies, but sub-Bohm diffusion may be
possible in turbulently amplified oblique magnetic fields
\citep[e.g.,][]{reville2013}, and has not been well-studied.
\note[Aaron]{I have no justification, and minimal sense, of whether this is
correct or not.  Any treatment/discussion of Bohm diffusion?  All the papers
seem to take it for granted} Different types of MHD turbulence, in a
quasi-linear approximation for particle motion, may give rise to a non-linear
energy scaling for diffusion coefficient \citep{giacalone1999, reynolds2004}.
Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence predict $D
\propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.  For gyroradius larger
than field coherence length, $\mu = 2$ may be relevant as well.
\note[Aaron]{Source?? Parizot mentions this in one sentence and cites nothing}

>>>>

%\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
%\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}

@@

\usepackage{amsmath}  % amsthm, amssymb
\usepackage{CJK}  % aas.org/authors/author-names-non-roman-alphabets
\usepackage{booktabs}
\usepackage{hyperref}

\newcommand*{\mt}{\mathrm}
\newcommand*{\unit}[1]{\;\mt{#1}}  % vemod.net/typesetting-units-in-latex
\newcommand*{\abt}{\mathord{\sim}} % tex.stackexchange.com/q/55701
\newcommand*{\ptl}{\partial}
\newcommand*{\del}{\nabla}

@@

\begin{document}
%\begin{CJK}{UTF8}{gbsn}

@@

\author{
Aaron Tran \altaffilmark{1,4},
% 陳 doesn't display?
% Also breaks emulateapj bibliography... toggle CJK env w/ AASTeX only
%Aaron Tran (陈宏裕)\altaffilmark{1,4},
Brian J. Williams\altaffilmark{1,5},
Robert Petre\altaffilmark{1},
Sean M. Ressler\altaffilmark{2},
Stephen P. Reynolds\altaffilmark{3}
}

@@

\altaffiltext{4}{CRESST, University of Maryland, College Park, MD 20742}
\altaffiltext{5}{NASA Postdoctoral Program Fellow}

@@

% What are these shock rims, what is this acceleration?
Forward shock accelerated electrons in young supernova remnants (SNRs) emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream, producing a shell-like morphology with bright X-ray and radio
rims/filaments due to line-of-sight projection \citep{koyama1995}.  Although
synchrotron emission due to accelerated electrons does not imply acceleration
of an unseen hadronic component, the prevailing theory of diffusive shock
acceleration (DSA) should operate on both protons and electrons.  Observations
of these synchrotron rims, with other lines of direct and indirect evidence,
have built a case for hadron and lepton acceleration up to $\unit{PeV}$
energies in young supernova remnants \citep{uchiyama2007, aharonian2004,
acero2010, ackermann2013}.  Efficient hadron acceleration in supernova remnant
shocks is a prime candidate source for galactic cosmic rays up to the
cosmic ray spectrum's ``knee'' \citep{vink2012}.
\note[Aaron]{the discussion of hadronic acceleration isn't really relevant,
just background information}

% What can we learn from these shocks?  Why are they interesting?
Spectral and spatial measurements of synchrotron rims can constrain physical
parameters of the shock acceleration process.  Many previous workers have
inferred strong magnetic field amplification at SNR shocks, as electrons must
rapidly radiate energy to account for the thinness of observed rims
\citep{bamba2003, vink2003, parizot2006}.  Furthermore, broadband synchrotron
synchrotron flux from supernova remnants steepens at X-ray energies
\citep{reynolds1999}, corresponding to a cut-off in the underlying electron
spectrum as predicted by diffusive shock acceleration \citep{webb1984}.
\note[Aaron]{question: which came first?  observation of synchrotron
steepening, or explanation/prediction of electron cut-off and hence synchrotron
roll-off?  Or, even, was the electron cut-off predicted but the observable
consequence of synchrotron roll-off not recognized until observations?} Many
fundamental questions about the shock acceleration process remain to be
answered.  Under what conditions do shocks accelerate particles efficiently?
How are magnetic fields amplified in such shocks?  \citet{reynolds2008} reviews
relevant observations and open questions to date.  The answers to these
questions are broadly relevant to many astrophysical shocks, such as Earth's
bow shock, stellar wind-blown bubbles, starburst galaxies \citep{heckman1990},
jets of active galactic nuclei, galaxy clusters \citep{van-weeren2010}, and
even cosmological shocks \citep{miniati2000, ryu2008}.
% Expand on these questions -- plasma turbulence, Alfven waves, wave damping
% behind the shock, upstream/downstream plasma interactions and instabilities
% These in turn affect plasma, CR dynamics -- how does the shock propagate and
% interact with the ISM?  Will we see a precursor due to diffusion and/or CR
% streaming?  How efficiently are CRs accelerated?

% What makes these shock rims?
The widths of these X-ray rims are controlled by a combination of
synchrotron losses, particle transport, and magnetic fields immediately
downstream of the shock.  Synchrotron losses depend on the initial electron
energy distribution and the gradual decrease of electron energies downstream of
the shock.  High energy electrons near the shock efficiently radiate harder
synchrotron X-ray photons, but decline in energy as they are transported away
from the shock; this may be seen in spectral softening downstream of the shock
\citep[e.g.,][]{cassam-chenai2007}.  The transport process is driven by bulk
plasma advection downstream of the shock and particle diffusion with respect to
bulk advection.  In general, diffusion allows higher energy electrons to
diffuse further upstream or downstream than would be expected from pure
advection.  Finally, the magnetic field strength may be quickly damped
downstream of the shock, so that electrons may not radiate as efficiently and
thin rims would reflect the spatial structure of the field, rather than
efficient particle acceleration (and losses) and/or efficient synchrotron
cooling \citep{pohl2005}.

% Whatever makes these shock rims also imposes energy dependence
Moreover, these controlling mechanisms predict different scalings for rim width
as a function of energy.  In the limiting case of constant magnetic field and
negligible particle diffusion, the rims are said to be synchrotron loss-limited
and rim widths should narrow with increasing photon frequency $\nu$ as
$\nu^{-1/2}$. Diffusion smears out rims at all energies with stronger effect at
higher energies, yielding a slower drop-off in rim widths when diffusion
dominates.  Magnetic damping, if at a length scale comparable to filament
widths, predicts comparatively energy-independent rim widths -- intuitively, if
the magnetic field turns off, synchrotron radiation turns off regardless of
electron energy.

% Magnetic damping?
Magnetic damping immediately behind the shock offers a tantalizing alternative
explanation for filament rims that requires less extreme magnetic field
amplification, and the possibility of damping in SNR shocks has not been fully
tested \citep{pohl2005, marcowith2010}.  \citet{cassam-chenai2007} examined
radio and X-ray synchrotron rim profiles, but found that neither damping nor
synchrotron losses matched radio profiles particularly well.  \citet{araya2010}
measured rims at multiple energy bands in Cas A, but suggested that the rims
only narrow more weakly than expected and did not consider magnetic damping.
\citet{rettig2012} gave model predictions for several historical SNRs and
proposed discriminating based on filament spectra -- the expectation is that
damped spectra are softer, loss-limited harder.  Recently, \citet{ressler2014}
further extended the idea of discriminating between damped or loss-limited
rims by measuring rim width energy dependence in X-ray energies and found that
rims consistently narrowed in the remnant of SN 1006, favoring synchrotron
loss-limited rims.

% Why Tycho's SNR
To further test these models, we follow \citet{ressler2014} (hereafter,
\citetalias{ressler2014}) by measuring rim widths at multiple energies in the
remnant of Tycho's 1572 supernova (hereafter, Tycho).  Tycho exhibits an
extensive shell of synchrotron-dominated thin rims around its periphery; the
rims show very little thermal emission, consistent with expansion into a low
density ISM \citet{williams2013}.  Tycho, being a nearby galactic SNR, is close
enough that its rims are easily resolved by \textit{Chandra} spatial
resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from an
archived \Chandra large project (PI: J. Hughes) also allows us to sample the
remnant rims quite finely.  Furthermore, Tycho has been a prime target of study
for determining whether hadrons are being accelerated in historic SNRs
\citep[and references therein]{morlino2012}; understanding the acceleration
process will bear upon our understanding of CR acceleration in Tycho.
\note[Aaron]{reword/cut?}

% Paper roadmap
Our procedure closely follows that of \citetalias{ressler2014}.
We first briefly review relevant transport models which fully account for
electron advection and diffusion with continuous synchrotron losses, as
considered by, e.g., \citet[and references therein]{berezhko2004} and
\citet{rettig2012}.  We selected and measured rim widths at several locations
around Tycho's forward shock, verifying that selected rims are free of thermal
line emission.  Using our model for particle transport (with DSA included, to
first order, in a simple exponentially cut-off injected electron spectrum), we
obtain estimates on magnetic field strength and diffusion coefficient
magnitude. We discuss the implications of our model fit results for
particle transport in Tycho, despite a significant degeneracy between
diffusion and synchrotron losses when diffusion is non-negligible.

@@

\note[Aaron]{I am a bit uncertain on the structure/order of presentation here,
particularly in presenting $\Ecut$ (which can be an independent observable?
but is not considered here).  I tried to put ``enough'' to independently
follow / re-derive all the model results.}
% TODO Chunk of text I don't know what to do with...
We consider two models for particle transport to our measurements of Tycho's
filament widths.  To best quantify width-energy dependence, we measure rim full
widths at half maximum (FWHMs) (Section~\ref{sec:fwhms}) and fit the
measurements to these models' predictions of rim FWHMs at multiple photon
energies.  \citetalias{ressler2014} give a fuller review of previous approaches
to characterizing filament widths, as well as a more thorough exposition of
model parameters and physical implications.

We use CGS (Gaussian) units throughout.

Any other introductory text -- emphasize that we back out two parameters,
possibly three or more.  COME BACK after writing magnetic damping bit.

@@

% TODO Choose names for these models and refer to them consistently, throughout
% TODO define ALL symbols, synchrotron constants, etc (somewhere state that CGS
%      notation is being used)
% TODO double check equations, exposition against Rettig/Pohl and others
% TODO review variable definitions when closer to final draft
\note[Aaron]{\citet{blandford1987} and other papers take a much more thorough
tack in deriving the relevant transport equations, drawing specifically from
plasma physics / DSA assumptions -- I suppose much material is not relevant or
condensed into our diffusion coefficient $D$ (w/ stated Bohm diffusion).
Is na\"ively citing generalized ``transport'' is sufficient here?
E.g., there is often a term of form $(E/3) (\del\cdot\vec{v}) (\ptl f/\ptl E)$,
neglected for steady downstream velocity (i.e., $\del\cdot\vec{v}=0$), which
would not arise out of our equations as stated.
See, e.g., equation (9) of \citet{skilling1975}.}
% Transport fundamentals
The energy and space distribution of electrons at a supernova remnant
controls the synchrotron rims we see in X-ray and radio.  We model electron
advection and diffusion from initial injection at the remnant's forward shock
assuming 1-D steady-state plane transport, with spatially homogeneous and
isotropic diffusion, as following the equation:
\begin{equation}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
\end{equation}
Here $f = f(E,x)$ is electron distribution as a function of electron energy $E$
and downstream distance $x$ (where the forward shock is at $x=0$ and $x>0$
towards the remnant's interior); $C$ is an arbitrary source/sink term, $D$ is
the diffusion coefficient, and $v_d$ is plasma velocity downstream of the
shock.  We consider only particle transport downstream of the shock ($x \geq
0$).  The source/sink term $C$ and diffusion coefficient $D$ conveniently
encapsulate all assumptions about the accelerated electron spectrum, shock
and magnetic field structure, and time/space evolution of the particle
distribution.  More sophisticated treatments may explicitly treat magnetic
fields and diffusion across the shock, plasma streaming instabilities and
particle losses, anisotropic diffusion, the DSA process and efficiency, and
other details in great depth \citep[e.g.,][and references therein]{reville2013,
bykov2014, ferrand2014}.

% Simple model
A first approximation is to let electrons have constant energy that is dumped
catastrophically after a synchrotron timescale $\tsynch = 1/(b B^2 E)$, where
$b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
vary in space as $B=B(x)$).  The sink term is $C = -f / \tsynch$, yielding:
\begin{equation} \label{eq:simp-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0 .
\end{equation}
No assumptions on the injected electron source term are necessary.
\citet{parizot2006} employed this model to derive estimates of magnetic fields,
diffusion coefficients, and electron spectrum cut-offs for several historical
SNRs.  Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f
\propto \exp(-x/a)$ where $a$ is a characteristic scale length.  The thin rim
FWHM predicted by equation~\eqref{eq:simp-mod} is:
\begin{equation} \label{eq:simp-fwhm}
    w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
\end{equation}
with $\beta$ a projection factor relating $w$ to $a$ as $w = \beta a$
\citep{berezhko2004, parizot2006}.  We take $\beta = 4.6$ assuming a spatially
exponential $f(E,x)$ and projection from a spherical shell, as derived by
\citet{ballet2006}.

% Full model
A more accurate model accounts for continuous synchrotron losses as electrons
are injected from an exponentially cut-off power-law electron distribution
(normalization $K_0$, cut-off energy $\Ecut$) and transported downstream:
\begin{align} \label{eq:full-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =\;
    &K_0 E^{-s} e^{-E/\Ecut} \delta(x) \nonumber \\
    &+ \frac{\ptl}{\ptl E} \left(bB^2E^2f\right) ;
\end{align}
see \citet{webb1984}, \citet{berezhko2004}, \citet{cassam-chenai2007},
\citet{morlino2010}, \citet{rettig2012}, and references therein.
\citet{zirakashvili2007} have derived a different electron spectrum with a
steeper $\exp\left(- \left(E/\Ecut\right)^2\right)$ cut-off, but we follow
\citetalias{ressler2014} in using $E^{-s} e^{-E/\Ecut}$ for conceptual
simplicity.  The cut-off energy is determined by the diffusion coefficient $D$,
which we address in Section~\ref{sec:diffcoeff}.  To determine rim profiles and
widths, we first numerically solve for electron distribution $f(E,x)$ using
Green's function solutions by \citet{lerche1980} and \citet{rettig2012}; these
solutions are given by \citetalias{ressler2014} using notation similar to that
used herein \note[Aaron]{wording}.  The electron distribution may then be
integrated to obtain synchrotron emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron emissivity
with $K_{5/3}(z)$ a modified Bessel function of the second kind
\citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
spherical remnant yields intensity as a function of radial coordinate $r$:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.  A model FWHM may then be calculated
from the resulting intensity profile.

% Moving on...
In what follows we consider both transport models, but primarily present
results from the more advanced model (equation~\eqref{eq:full-mod}) as we find
that the qualitative behavior of both models is comparable.

@@

Much previous work has assumed Bohm-like diffusion in plasma downstream of the
shock.  Bohm diffusion assumes that the particle mean free path $\lambda$ is
equal to the gyroradius $r_g = E/(eB)$, yielding diffusion coefficient
$D_{\mt{B}} = \lambda c / 3 = c E / (3 e B)$; here $c$ is the speed of light,
$E$ is particle energy, $e$ is the elementary charge, and $B$ is magnetic
field.  Bohm-like diffusion introduces a free prefactor $\eta$ such that
$\lambda = \eta r_g$ allows for varying diffusion; however, Bohm diffusion at
$\eta = 1$ is commonly considered a lower limit on the diffusion coefficient at
all energies.
\note[Aaron]{for self-edification, any justification / derivation of this
result?  All the papers seem to take it for granted}
However, different types of MHD turbulence may give rise to a non-linear energy
scaling for diffusion coefficient \citep{giacalone1999, reynolds2004}.
Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence, with a
quasi-linear approximation for particle motion,
\note[Aaron]{I don't really know what this means}
predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
Particle gyroradii larger than field coherence length may to $D \propto E^{2}$
\note[Aaron]{Source?? Parizot mentions this in one sentence and cites nothing.
I have no idea what this means.}
